Solar wind discontinuities spatial evolution in the outer heliosphere

### 2024-05-13 article.qmd
update

@@

@@

@@

$$
J_m = - \frac{1}{\mu_0 V_n} \frac{d B_m}{d t},
$$

@@

>>>>

Because the discontinuities may have different spatial scale at different radial distances from the Sun, we repeat the search procedure with time lags $T = 10, 20, 30, 40, 50, 60$ s, and combine the identified ID events together to establish the event list.
Discontinuities with spatial scales larger than $60$ s are not considered in this study, however it could be argued that they are not significant in the outer heliosphere if they follow the trend with decreasing number of IDs with increasing spatial scale. @fig-ljFit also indicates that the spatial scale of IDs does not vary significantly with the radial distance from the Sun.

> To cover IDs at different spatial scales, we repeat the search procedure with time lags T = 10, 20, 30, 40, 50, 60s, and combine the identiﬁed ID events together to establish the event list.

@@

![](figures/l_j_fit)

![](figures/l_j_fit_xscale_log.png){#fig-ljFit}

@@

In @vaskoKineticscaleCurrentSheets2022 paper, CS thickness is estimated by the formula $d = \frac{\Delta B_l}{2 \mu_0 < J_m> }$. Because of @eq-j, $d = \frac{\Delta B_l}{2 \mu_0 < J_m> } = \frac{\Delta B_l V_n }{2 <\frac{d B_m}{ d t} >}$

@@

$$
J_m = - \frac{1}{\mu_0 V_n} \frac{d B_m}{d t},
$$ {#eq-j}

@@

![](figures/l_j_fit_taus)

![](figures/l_j_fit_taus_xscale_log)
